Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/introduction.tex
modify introduction and methodology

Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
one is the classification model that directly maps an input into a most likely label, and
the other one is the similarity  model  that searches a label whose associated data is most similar to
an input.

The   first  one,  \emph{text  classification},  includes  classic  long  text
classification  and  short  text  classification  in  this  scenario.  Besides
traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
boosting  tree \cite{tu2005probabilistic},  many work
\cite{wen2016network}  choose  neural  network  such  as  convolutional neural
networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
and       long       short       term       memory       networks      (LSTMs)
\cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
extracting  semantic  feature from limited amount of words. Their common model
structure  is  adding  a  softmax classifier as the final layer and mapping to
labels.  Another  two  interesting lines of work, label-word joint models, and
joint  NER  and  classification  are  discussed  in  the related work section.
Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
\cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
powerful  in  solving  many  NLP  tasks  including  short-text  classification
\cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
\cite{yu2018diverse},     pre-trained     model    based    on    transformers
\cite{vaswani2017attention} tends to do more
help to reducing the negative effects brought by scarcity of training data.

The  second  one,  \emph{similarity model} is also called sentence-pair model.
Its  motivation  originates  from  the idea of Information Retrieval (IR) based
chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
(Question-Answer)  pairs dataset and user query Q, the IR based conversational
system will look up in the Q-A dataset for the pair (Q', A') that best matches
query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
\cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
corpus  of  semantic  similarity  identification task can be applied for being
used  as  a  tool  to  identify  the class with highest semantic similarity to
customer's    query.    A    common    model    structure    of    pre-trained 
sentence-pair model is based on multiple cross-attention
mechanism  \cite{barkan2020scalable}. Due to
the   fact   that   many   experiment   results   have   shown   that  RoBERTa
\cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
results  on  both  text  classification and sentence-pairs semantic similarity
tasks, we choose RoBERTa as an important baseline approach in this paper.

>>>>

Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
one is based on the \emph{(text) classification model} that directly maps an input into a most likely label, and
the other one is based on the \emph{(text) similarity  model}  that searches a label whose associated data is most similar to
an input.

The   first  one,  \emph{classification model},  includes  classic  long  text
classification  and  short  text  classification  in  this  scenario.  Besides
traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
boosting  tree \cite{tu2005probabilistic},  many work
\cite{wen2016network}  choose  neural  network  such  as  convolutional neural
networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
and       long       short       term       memory       networks      (LSTMs)
\cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
extracting  semantic  features from limited amount of words. Their common model
structure  is  adding  a  softmax classifier as the final layer and mapping to
labels.  Another  two  interesting lines of work, label-word joint models, and
joint  NER  and  classification  are  discussed  in  the related work section.
Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
\cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
powerful  in  solving  many  NLP  tasks  including  short-text  classification
\cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
\cite{yu2018diverse},     pre-trained     model    based    on    transformers
\cite{vaswani2017attention} tends to be more helpful to reduce the negative effects brought by scarcity of training data.

The  second  one,  \emph{similarity model},  is also called sentence-pair model.
Its  motivation  originates  from  the idea of retrieval based
chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Given  a  Q-A
(Question-Answer)  pairs dataset and a user query Q, the retrieval based conversational
system will search from the Q-A dataset  the most matched pair (Q', A') 
through  semantic  analysis  and  return  A'  as  the  answer  to Q
\cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
corpus  can be employed  to  identify  the class with highest semantic similarity to
customer's    query.    A    common    model    structure    of    pre-trained 
sentence-pair model is based on multiple cross-attention
mechanism  \cite{barkan2020scalable}. Due to
the   fact   that   many   experiment   results   have   shown   that  RoBERTa
\cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
results  on  both  text  classification and sentence-pairs semantic similarity
tasks, we choose RoBERTa as one of the baselines in this paper.

### 2020-09-10 chatbot_classification/aaai_2021/methodology.tex
modified:   experiments.tex   modified:   methodology.tex
modify introduction and methodology

\section{Methodology}
In  this section, we describe our proposed system, a similarity model fused with
a classification  model (SFC). We propose two approaches to implement this idea,
two-stage SFC, and its more compact version joint SFC.

@@

\subsubsection*{
  Stage 1: classification model for providing top-K candidate class labels
} 
We  can  use any auxiliary text classification model or tool,
such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
provide  top-K  most  related  class  labels. These selected class labels will
later  be  used to sample sentence pairs of both positive samples and negative
samples  for  stage  2.

@@

\begin{table*}
  \begin{centering}
    \scalebox{0.9}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

>>>>

\section{Methodology}
In  this section, we describe our proposed SFC. We propose two approaches to implement this idea,
two-stage SFC, and its more compact version joint SFC.

@@

\subsubsection*{
  Stage 1: classification model for providing top-K candidate class labels
} 
We  can  use any auxiliary text classification model or tool,
such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
provide  top-K  most  related  class  labels. These selected class labels will
later  be  used to sample sentence pairs of both positive and negative
samples  for  stage  2.

@@

\begin{table*}
  \begin{centering}
    \scalebox{0.9}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 17 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}
